---
title: "Madagascar iCCM Endline"
author: "Dean and Friends"
date: "`r format(Sys.time(), '%A %d %B %Y')`"
output: 
  html_document:
    code_folding: hide
    highlight: zenburn
    number_sections: yes
    theme: spacelab
    toc: yes
    toc_collapse: no
    toc_depth: 4
    toc_float: yes
    css: C:/Users/omp2/OneDrive - CDC/Madagascar_10_12_19/endline/mada_2_the_sequel/style.css
    includes:
    #  before_body: phase_2_head.html
      in_header: header.html
---


<div class="watermark">PRELIMINARY</div>
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      collapse = TRUE,
                      fig.width = 7,
                      fig.height = 6,
                      dpi = 500,
                      warning = FALSE,
                      message = FALSE)

```




<!-- ======================================================= -->
<!-- ======================================================= -->
<!-- ======================================================= -->

# Project Overview {.tabset .tabset-fade .tabset-pills}

# Loading stuff {.tabset .tabset-fade .tabset-pills}
## Packages
```{r}
pacman::p_load(tmap, 
               Hmisc,
               here,
               sf, 
               survey,
               janitor, 
               linelist, 
               lubridate, 
               purrr,
               tidyverse)
```

## Functions
Bespoke functions are sourced through a separate R script for ease of reference.
It is tempting to place functions adjacent to where used in the scripts, but this 
can make them difficult to find when needing to alter/review.
```{r}
source(functions.R)
```

## Data
Data cleaning and variable creation are also sourced through R scripts to keep 
wrangling/manipulations centrally located.
```{r}
source(data_cleaning.R)
source(new_variables.R)
```

